---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PFASMetabolite

<!-- badges: start -->
<!-- badges: end -->

The goal of PFASMetabolite is to detect peak features of PFAS metabolites from zebrafish

## Installation

You can install the the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("huiUofT/PFASmetabolite")
```
## Example

This is a basic example which shows you how to solve a common problem:

Step 1: loading packages
```{r, message=FALSE, warning=FALSE}
  rm(list=ls())
  library(xcms)
  library(devtools)
  library(PFASMetabolite)
  
  #'set up the path
  setwd("C:/Rprogram/EHP_PFAS/PFASmetabolite")
```

Step 2: extracting peak features from raw mass spectrometry data
```{r, include=FALSE}
  #'10000 is the intensity cutoff to extract peaks, 2.5 ppm is the mass tolerance for peak detection
  peak<-Peakextract(100000,2.5)
```

Step 3: finding out peaks features significantly higher in treatment groups than controls
```{r, message=FALSE, warning=FALSE}
  #'Defining the keywords to extract data from control or treatment
  control<-'S_6'
  treat<-'S18_6'
  
  #'10 is the fold change between control and treatment groups, 0.05 is the p value cutoff
  peaks<-DiffPeaks(peak, 10, 0.05,control,treat)
```
Step 4: identifying primary isotopic peaks, and remove redudant isotopic peaks
```{r, message=FALSE, warning=FALSE}
  #2 ppm is the mass tolerance to find isotopic peaks
  #'0.80 is the correlation coefficient to extract isotopic peaks
  #'3 is the intensity ratio cutoff between primary and other isotopic peaks
  peaks.iso<-FindIsotope(peaks,2,0.80,0.3)
```
